%-------------------------
% Resume in Latex
% Author : Ganesh Shinde
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://ganesh-shinde.netlify.app/}{\Large Ganesh Shinde}} & Email :  \href{mailto:ganeshshinde.tyjo@gmail.com}{ganeshshinde.tyjo@gmail.com}\\
  \href{https://ganesh-shinde.netlify.app/}{Portfolio |}
  \href{https://www.linkedin.com/in/ganesh-tyjo/}{LinkedIn |}
  \href{https://github.com/ganesh-tyjo/}{GitHub}& Mobile :  +91-8097281710 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {B. N. Bandodkar College}{Thane, India}
      {(Mumbai University; Bachelor of Science in Information Technology);  Grade: A }{2014 - 2017}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{}{
     \textbf{Languages}{: C\#, SQL, LINQ, Javascript, JQuery, HTML, CSS, SCSS }
     }
 \resumeSubItem{}{
     \textbf{Technologies and Frameworks}{: ASP.NET MVC, .NET Core MVC, Entity Framework Core, REST API, Kendo }
    }
  \resumeSubItem{}{
     \textbf{Database Technology}{: Microsoft SQL Server }
    }
  \resumeSubItem{}{
     \textbf{Tools}{: Git, Git Hub, TortoiseSVN, Parcel, Gulp }
    }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience (5+ Years)}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Creative IT India}{Navi Mumbai, India}
      {Sr. Software Engineer}{Sep 2021 - Present}
      \resumeItemListStart
      \resumeItem{}
          {I developed a web platform using .Net Core to enhance and optimize the child support service workflow.}
        \resumeItem{}
          {Overseen the implementation and management of an efficient ETL platform to streamline data extraction, transformation, and loading processes.}
        \resumeItem{}
          {Successfully spearheaded the creation of multiple Proof of Concepts (POCs) leveraging cutting-edge tools like Twilio Conversations and GraphQL, demonstrating their versatility and unlocking new possibilities in communication and data management.}
      \resumeItemListEnd
      
    \resumeSubheading
      {KANTAR}{Mumbai, India}
      {Software Engineer}{Jun 2018 - Sep 2021}
      \resumeItemListStart
      \resumeItem{}
        {In response to the COVID lockdown, rapidly developed a web platform within a tight timeframe to facilitate online interviews, replacing the traditional face-to-face data collection process. Implemented a seamless incentive distribution system, resulting in enhanced reach, increased revenue, and improved overall performance.}
      \resumeItem{}
          {Implemented data cleaning automation by developing robust applications using the .Net framework, resulting in enhanced data accuracy and significant reduction in time consumption. }
    \resumeItem{}
    {Successfully applied Agile methodologies throughout the development process, resulting in highly efficient workflows and delivering exceptional results.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Align Child Support}
    { - Empowered single parents by providing a user-friendly web platform built on .NET Core, streamlining the entire child support process. From initial application to tracking payments, the platform facilitated the smooth handling of monetary assistance from the partner to support and care for their children, even after the termination of the relationship. }
    \resumeSubItem{Dataport}
    { - Managed a lightweight, configurable, and secure enterprise ETL platform packed with advanced features. This platform offers an efficient UI-based SQL editor for seamless data manipulation. Additionally, it enables real-time tracking of extraction and load statuses, ensuring a smooth and transparent ETL process.}
    \resumeSubItem{KoolP}
    { - During the COVID-19 lockdown, developed a robust web platform that seamlessly transitioned the data collection process from face-to-face interviews to online interviews. Integrated the platform with NIPO (for online surveys) and XOXODAY (for incentives) through their APIs, enabling efficient survey administration and timely distribution of incentives to respondents.}
    \resumeSubItem{Respondent DB}
    { - Revolutionized the respondent selection process for interviews by creating a user-friendly web application based on ASP.NET MVC. Implemented the ability to add specific criteria for retrieving respondents from a large centralized data source, simplifying the selection process. The application also included features such as uploading new respondents and maintaining a comprehensive history of respondents, tracking their participation in past surveys.}
    \resumeSubItem{Media XPress}
    { - Designed and developed a dynamic dashboard using WPF (Windows Presentation Foundation) that facilitated the creation of tables, visually represented data reports, including charts and heatmaps. This powerful tool greatly enhanced the analysis of TV viewership trends, providing an intuitive and comprehensive way to analyze data and gain insights quickly.}
  \resumeSubHeadingListEnd

%---------------------------------------
\section{Accomplishments}
 \resumeSubHeadingListStart
 \resumeSubItem{}
    {Awarded Star Performer of Q1 2022 by Creative IT India for exceptional contributions and outstanding performance.}
 \resumeSubHeadingListEnd
%-------------------------------------
 \end{document}